---
title: "Untitled"
output: html_document
---




### Question 1:

Using a loop, print the integers from 1 to 50. 
```{r}
x=1:50
for (i in 1:length(x)){
  print(i)
}

```


### Question 2:

A.  Using a loop, add all the integers between 0 and 1000.
```{r}

y=1:999
final=0
for (i in y){
  final<-sum(i)+final
}
 
```


B. Now, add all the EVEN integers between 0 and 1000 (hint: use seq())
```{r}
even=0
z=seq(2,98,by=2)
for (i in z){
  even<-sum(i)+even
}
```


C. Now, repeat A and B WITHOUT using a loop.
```{r}
## Part A repeat without using a loop
t=1:999
part_a_no_loop<-sum(t)

## Part B repeat without using a loop
u=seq(2,98,by=2)
part_b_no_loop<-sum(u)
```


### Question 3:

Here is a dataframe of survey data containing 5 questions :

```{r, eval=FALSE}
survey <- data.frame(
                     "participant" = c(1, 2, 3, 4, 5, 6),
                     "q1" = c(5, 3, 2, 7, 11, 0),
                     "q2" = c(4, 2, 2, 5, -10, 99),
                     "q3" = c(-4, -3, 4, 2, 9, 10),
                     "q4" = c(-30, 5, 2, 23, 4, 2),
                     "q5" = c(88, 4, -20, 2, 4, 2)
                     )
```
The response to each question should be an integer between 1 and 5. Obviously, we have some bad values in the dataframe. The goal of this problem is to fix them.

A. Using a loop, create a new dataframe called survey.clean where all the invalid values (those that are not integers between 1 and 5) are set to NA.
```{r}
x=survey[survey>5|survey<1]
survey.clean<-data.frame(
                     "q1" = c(5, 3, 2, 7, 11, 0),
                     "q2" = c(4, 2, 2, 5, -10, 99),
                     "q3" = c(-4, -3, 4, 2, 9, 10),
                     "q4" = c(-30, 5, 2, 23, 4, 2),
                     "q5" = c(88, 4, -20, 2, 4, 2))
for(i in 1:length(x)){ 
    survey.clean[survey.clean==x[i]]<-NA
}

cbind(survey$participant,survey.clean)

```


B. Now, again using a loop, add a new column to the dataframe called “invalid.answers” that indicates, for each participant, how many bad answers they gave.

```{r}
survey.clean %>%
  mutate(invalid.answers= rowSums(is.na(survey.clean)))
```

